TBD

### 2021-02-25 outputs/paper/paper.Rmd
Updated Appendix with survey screenshots and funding details

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
    fig_caption: yes
header-includes:
    #- \usepackage[labelformat=empty]{caption}
toc: FALSE
bibliography: references.bib
---

@@

  kable(chi_df,
        digits = 3,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
             general_title = "") %>%
    column_spec(1, bold = T, width = "8em") %>%
    column_spec(2, width = "6em") %>%
    column_spec(3, width = "6em") %>%
    column_spec(4, width = "6em")
}
```

@@

* the largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%);
* most restaurants are of medium or larger scale, with seating areas of at least 30; 
* a majority of the restaurants are relatively new (1-4 years old); 
* fast-food/quick service restaurants are most common, followed by casual dining, and then fine dining;
* and UberEats is the most popular food courier service in the city.

@@

@@

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Najma Osman, Rachit Srivastava, Morgaine Westin, and Bongju Yoo"
thanks: "Code and data are available at: https://github.com/bonjwow/covid-shut-down"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
    fig_caption: yes
header-includes:
    #- \usepackage[labelformat=empty]{caption}
toc: FALSE
bibliography: references.bib
---

@@

  kable(chi_df,
        digits = 3,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001",
             general_title = "") %>%
    column_spec(1, bold = T, width = "8em") %>%
    column_spec(2, width = "6em") %>%
    column_spec(3, width = "6em") %>%
    column_spec(4, width = "6em")
}
```
# Introduction

@@

* the largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%);
* most restaurants are of medium or larger scale, with seating areas of at least 30; 
* a majority of the restaurants are relatively new (3 years or less); 
* fast-food/quick service restaurants are most common, followed by casual dining, and then fine dining;
* and UberEats is the most popular food courier service in the city.

@@

# Discussion

## Overview of Findings

## Limitations and Future Directions

@@

## Survey

```{r survey1, echo = FALSE, message = FALSE, fig.cap = "Screenshot of Google Forms Survey Questions 1-8", out.width="90%"}
knitr::include_graphics("survey/01.png")
```

```{r survey2, echo = FALSE, message = FALSE, fig.cap="Screenshot of Google Forms Survey Questions 9-16", out.width="90%"}
knitr::include_graphics("survey/02.png")
```

## Funding Acknowledgement

We would like to thank the Ontario Government for generously providing Petit Poll with $240,000 CAD in funding to carry out this study. The funding was used to provide compensation to restaurants for participating in the intervention. A sample size of 200 for the intervention condition was selected based on this amount, in which each restaurant who participated in the intervention received $1200. A total of 150 restaurants participated in the intervention and received payment, making the total amount of funding spent during the study $180,000 CAD.
